Price of Anarchy for Mean Field Games

### 2018-07-23 PoA.tex
update prop 4 to be continue

\begin{proof}

	When $b_2 \to \infty$, we have 
	\begin{equation*}
	\begin{array}{l}
	\lambda^{b_2} \to \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}\\
	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty} \\
	A^{u}, A^{w}, C^w, D^w, A^{\eta}, C^{\eta}, D^{\eta} \text{ are independent of } b_2
	\end{array}
	\end{equation*}
	Moreover
	\begin{IEEEeqnarray*}{rCl}
		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} &=& \frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} + \frac{(A^u)^2}{(b_2+\bar{b}_2)^2} }\\
		&\xrightarrow[b_2 \to \infty]{}& \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}}
	\end{IEEEeqnarray*}
	Thus we have $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$ and for any $t \in [0,T)$,
	$$\displaystyle  e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} \xrightarrow[b_2 \to \infty]{} 0.$$
	From the explicit formula (\ref{eq:riccati_ut_sol}) of $u_t^{b_2}$, we can compute the limit of $(b_2 + \bar{b}_2) u_t^{b_2}$ for any $t \in [0,T)$ by dividing the numerator with $(b_2 + \bar{b}_2)$ and the denominator with $(b_2)+\bar{b}_2)^2$, namely
	\begin{IEEEeqnarray*}{rCl}
		(b_2 + \bar{b}_2) u^{b_2}_t &=& \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
		{\displaystyle \left(\frac{- \delta^{-,b_2}_u}{(b_2 + \bar{b}_2)^2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} \right) + \left(\frac{\delta^{+,b_2}_u}{(b_2 + \bar{b}_2)^2} - \frac{D^{u,b_2} }{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)}  } \nonumber \\
		&&\\
		&\xrightarrow[b_2 \to \infty]{}& \quad (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_u^{b_2 \to \infty}}  =: c_u
	\end{IEEEeqnarray*}
	Idem, we can have for any $t \in [0,T)$,
	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} }.$$
%	and for any $t \in [0,T)$,
%	$$ b_2 \eta_t^{b_2} \xrightarrow[b_2 \to \infty]{} (r+ \bar{r}) c_{\delta_\eta^{b_2 \to \infty}} =: c_5, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} = \sqrt{\frac{q+\bar{q}}{r + \bar{r}}}.
%	$$

>>>>

\begin{proof}
	If $\bar{b}_2 = 0$ then 
	$$\lambda = \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}$$ which is a constant independent of $b_2$,
	otherwise when $b_2 \to \infty$, we still have
	$ \lambda^{b_2} \to \lambda^{b_2 \to \infty}$.	
	For other coefficients, in the case when $b_2 \to \infty$ we have 
	\begin{equation*}
	\begin{array}{l}
	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty}
	\end{array}
	\end{equation*}
	and $A^{u}, (A^{w}, C^w, D^w), (A^{\eta}, C^{\eta}, D^{\eta})$ are independent of  $b_2$.

	Moreover
	\begin{equation*}
		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} = \frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} + \frac{(A^u)^2}{(b_2+\bar{b}_2)^2} } \xrightarrow[b_2 \to \infty]{} \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}}
	\end{equation*}
	Thus we have $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$ and for any $0 \leq t < T$:
	$$\displaystyle  e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} \xrightarrow[b_2 \to \infty]{} 0.$$
	From the explicit formula (\ref{eq:riccati_ut_sol}) of $u_t^{b_2}$, we can compute the limit of $(b_2 + \bar{b}_2) u_t^{b_2}$ for any $t \in [0,T)$ by dividing the numerator with $(b_2 + \bar{b}_2)$ and the denominator with $(b_2)+\bar{b}_2)^2$, namely
	\begin{IEEEeqnarray*}{rCl}
		(b_2 + \bar{b}_2) u^{b_2}_t &=& \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
		{\displaystyle \left(\frac{- \delta^{-,b_2}_u}{(b_2 + \bar{b}_2)^2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} \right) + \left(\frac{\delta^{+,b_2}_u}{(b_2 + \bar{b}_2)^2} - \frac{D^{u,b_2} }{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)}  } \nonumber \\
		&&\\
		&\xrightarrow[b_2 \to \infty]{}& \quad (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_u^{b_2 \to \infty}}  =: c_u
	\end{IEEEeqnarray*}
	Idem, we can have for any $t \in [0,T)$,
	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} }.$$
%	and for any $t \in [0,T)$,
%	$$ b_2 \eta_t^{b_2} \xrightarrow[b_2 \to \infty]{} (r+ \bar{r}) c_{\delta_\eta^{b_2 \to \infty}} =: c_5, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} = \sqrt{\frac{q+\bar{q}}{r + \bar{r}}}.
%	$$
